\rhead{\xiaowuhao参考文献}
\renewcommand{\refname}{\song\xiaoerhao参考文献}
\begin{thebibliography}{200}
{
\setlength{\itemsep}{-2pt}
%\setlength{\itemindent}{-1em}
{\renewcommand\baselinestretch{1.0}\selectfont
\wuhao

\bibitem{Villavicencio14}Villavicencio G. Software maintenance like maintenance in other engineering disciplines[C]//Proceedings of the 22nd ACM SIGSOFT International Symposium on Foundations of Software Engineering. ACM, 2014: 853-856.
\bibitem{Szabo15}Szabo C. Novice code understanding strategies during a software maintenance assignment[C]//Proceedings of the 37th International Conference on Software Engineering-Volume 2. IEEE Press, 2015: 276-284.
\bibitem{Rovegard08}Rovegard P, Angelis L, Wohlin C. An empirical study on views of importance of change impact analysis issues[J]. IEEE Transactions on Software Engineering, 2008 (4): 516-530.
\bibitem{Kim07}Kim S, Ernst M D. Prioritizing warning categories by analyzing software history[C]//Proceedings of the Fourth International Workshop on Mining Software Repositories. IEEE Computer Society, 2007: 27.
\bibitem{Bradley11}Bradley A W J, Murphy G C. Supporting software history exploration[C]//Proceedings of the 8th working conference on mining software repositories. ACM, 2011: 193-202.
\bibitem{Wittenhagen16}Wittenhagen M, Cherek C, Borchers J. Chronicler: Interactive exploration of source code history[C]//Proceedings of the 2016 CHI Conference on Human Factors in Computing Systems. ACM, 2016: 3522-3532.
\bibitem{Ambros08}Ambros M, Gall H, Lanza M, et al. Analysing software repositories to understand software evolution[M]//Software evolution. Springer, Berlin, Heidelberg, 2008: 37-67.
\bibitem{Thomas14}Thomas S W, Adams B, Hassan A E, et al. Studying software evolution using topic models[J]. Science of Computer Programming, 2014, 80: 457-479.
\bibitem{Gousios08}Gousios G, Kalliamvakou E, Spinellis D. Measuring developer contribution from software repository data[C]//Proceedings of the 2008 international working conference on Mining software repositories. ACM, 2008: 129-132.
\bibitem{Dabbish12}Dabbish L, Stuart C, Tsay J, et al. Social coding in GitHub: transparency and collaboration in an open software repository[C]//Proceedings of the ACM 2012 conference on computer supported cooperative work. ACM, 2012: 1277-1286.
\bibitem{Canfora05}Canfora G, Cerulo L. Impact analysis by mining software and change request repositories[C]//Software Metrics, 2005. 11th IEEE International Symposium. IEEE, 2005: 9 pp.-29.
\bibitem{Kagdi10}Kagdi H, Gethers M, Poshyvanyk D, et al. Blending conceptual and evolutionary couplings to support change impact analysis in source code[C]//Reverse Engineering (WCRE), 2010 17th Working Conference on. IEEE, 2010: 119-128.
\bibitem{Sun15}Sun X, Li B, Leung H, et al. Msr4sm: Using topic models to effectively mining software repositories for software maintenance tasks[J]. Information and Software Technology, 2015, 66: 1-12.
\bibitem{Wong15}Wong E, Liu T, Tan L. Clocom: Mining existing source code for automatic comment generation[C]//Software Analysis, Evolution and Reengineering (SANER), 2015 IEEE 22nd International Conference on. IEEE, 2015: 380-389.
\bibitem{Huang17}Huang Y, Zheng Q, Chen X, et al. Mining version control system for automatically generating commit comment[C]//Proceedings of the 11th ACM/IEEE International Symposium on Empirical Software Engineering and Measurement. IEEE Press, 2017: 414-423.
\bibitem{Okutan14}Okutan A, Yildiz O T. Software defect prediction using Bayesian networks[J]. Empirical Software Engineering, 2014, 19(1): 154-181.
\bibitem{Moeyersoms15}Moeyersoms J, de Fortuny E J, Dejaeger K, et al. Comprehensible software fault and effort prediction: A data mining approach[J]. Journal of Systems and Software, 2015, 100: 80-90.
\bibitem{Nelson04}Nelson S, Schumann J. What makes a code review trustworthy?[C]//System Sciences, 2004. Proceedings of the 37th Annual Hawaii International Conference on. IEEE, 2004: 10 pp.
\bibitem{Edmundson13}Edmundson A, Holtkamp B, Rivera E, et al. An empirical study on the effectiveness of security code review[C]//International Symposium on Engineering Secure Software and Systems. Springer, Berlin, Heidelberg, 2013: 197-212.
\bibitem{McIntosh16}McIntosh S, Kamei Y, Adams B, et al. An empirical study of the impact of modern code review practices on software quality[J]. Empirical Software Engineering, 2016, 21(5): 2146-2189.
%\bibitem{孙12}孙小兵, 李斌, 陈颖, 等. 软件修改影响分析研究与进展[J]. 电子学报, 2014, %42(12): 2467-2476.
\bibitem{}Bohner S A, Arnold R S. Software change impact analysis for design evolution[C]//Proceedings of 8th International Conference on Maintenance and Re-engineering. IEEE CS Press Los Alamitos, CA, 1991: 292-301.


\bibitem{Bouktif06}Bouktif S, Gueheneuc Y G, Antoniol G. Extracting change-patterns from cvs repositories[C]//Reverse Engineering, 2006. WCRE'06. 13th Workingi Conference on. IEEE, 2006: 221-230.

\bibitem{Ying04}Ying A T T, Murphy G C, Ng R, et al. Predicting source code changes by mining change history[J]. IEEE transactions on Software Engineering, 2004, 30(9): 574-586.

\bibitem{Tomas05}Zimmermann T, Zeller A, Weissgerber P, et al. Mining version histories to guide software changes[J]. IEEE Transactions on Software Engineering, 2005, 31(6): 429-445.

\bibitem{Ajienka18}Ajienka N, Capiluppi A, Counsell S. An empirical study on the interplay between semantic coupling and co-change of software classes[J]. Empirical Software Engineering, 2018, 23(3): 1791-1825.

\bibitem{Jaafar14}Jaafar F, Guéhéneuc Y G, Hamel S, et al. Detecting asynchrony and dephase change patterns by mining software repositories[J]. Journal of Software: Evolution and Process, 2014, 26(1): 77-106.

\bibitem{Vaucher08}Vaucher S, Sahraoui H, Vaucher J. Discovering new change patterns in object-oriented systems[C]//Reverse Engineering, 2008. WCRE'08. 15th Working Conference on. IEEE, 2008: 37-41.

\bibitem{Fluri08}Fluri B, Giger E, Gall H C. Discovering patterns of change types[C]//Proceedings of the 2008 23rd IEEE/ACM International Conference on Automated Software Engineering. IEEE Computer Society, 2008: 463-466.

\bibitem{Thongtanunam15}Thongtanunam P, Tantithamthavorn C, Kula R G, et al. Who should review my code? A file location-based code-reviewer recommendation approach for modern code review[C]//Software Analysis, Evolution and Reengineering (SANER), 2015 IEEE 22nd International Conference on. IEEE, 2015: 141-150.

\bibitem{Kononenko15}Kononenko O, Baysal O, Guerrouj L, et al. Investigating code review quality: Do people and participation matter?[C]//Software Maintenance and Evolution (ICSME), 2015 IEEE International Conference on. IEEE, 2015: 111-120.

\bibitem{Baysal16}Baysal O, Kononenko O, Holmes R, et al. Investigating technical and non-technical factors influencing modern code review[J]. Empirical Software Engineering, 2016, 21(3): 932-959.
\bibitem{Murali17}Murali V, Chaudhuri S, Jermaine C. Bayesian specification learning for finding API usage errors[C]//Proceedings of the 2017 11th Joint Meeting on Foundations of Software Engineering. ACM, 2017: 151-162.
\bibitem{Mills17}Mills C. Automating traceability link recovery through classification[C]//Proceedings of the 2017 11th Joint Meeting on Foundations of Software Engineering. ACM, 2017: 1068-1070.
\bibitem{Rath18}Rath M, Rendall J, Guo J L C, et al. Traceability in the wild: automatically augmenting incomplete trace links[C]//Proceedings of the 40th International Conference on Software Engineering. ACM, 2018: 834-845.
\bibitem{Karim17}Karim S, Warnars H L H S, Gaol F L, et al. Software metrics for fault prediction using machine learning approaches: A literature review with PROMISE repository dataset[C]//Cybernetics and Computational Intelligence (CyberneticsCom), 2017 IEEE International Conference on. IEEE, 2017: 19-23.
\bibitem{Shimonaka16}Shimonaka K, Sumi S, Higo Y, et al. Identifying Auto-Generated Code by Using Machine Learning Techniques[C]//Empirical Software Engineering in Practice (IWESEP), 2016 7th International Workshop on. IEEE, 2016: 18-23.
\bibitem{Nguyen14}Nguyen A T, Nguyen H A, Nguyen T T, et al. Statistical learning approach for mining API usage mappings for code migration[C]//Proceedings of the 29th ACM/IEEE international conference on Automated software engineering. ACM, 2014: 457-468.
\bibitem{Mario14}Linares-Vásquez M, McMillan C, Poshyvanyk D, et al. On using machine learning to automatically classify software applications into domain categories[J]. Empirical Software Engineering, 2014, 19(3): 582-618.

\bibitem{Michall99}Michail A. Data mining library reuse patterns in user-selected applications[C]//ase. IEEE, 1999: 24.

\bibitem{Lin13}Lin Y, Dig D. Check-then-act misuse of java concurrent collections[C]//2013 IEEE Sixth International Conference on Software Testing, Verification and Validation. IEEE, 2013: 164-173.

\bibitem{Holmes06}Holmes R, Walker R J, Murphy G C. Approximate structural context matching: An approach to recommend relevant examples[J]. IEEE Transactions on Software Engineering, 2006 (12): 952-970.

\bibitem{Bruch09}Bruch M, Monperrus M, Mezini M. Learning from examples to improve code completion systems[C]//Proceedings of the the 7th joint meeting of the European software engineering conference and the ACM SIGSOFT symposium on The foundations of software engineering. ACM, 2009: 213-222.

\bibitem{Uddin11}Uddin G, Dagenais B, Robillard M P. Analyzing temporal API usage patterns[C]//Proceedings of the 2011 26th IEEE/ACM International Conference on Automated Software Engineering. IEEE Computer Society, 2011: 456-459.

\bibitem{Canfora11}Canfora G, Ceccarelli M, Cerulo L, et al. How long does a bug survive? an empirical study[C]//2011 18th Working Conference on Reverse Engineering. IEEE, 2011: 191-200.

\bibitem{Canfora09}Canfora G, Cerulo L, Di Penta M. Tracking your changes: A language-independent approach[J]. IEEE Software, 2009, 26(1).

\bibitem{Thummalapenta10}Thummalapenta S, Cerulo L, Aversano L, et al. An empirical study on the maintenance of source code clones[J]. Empirical Software Engineering, 2010, 15(1): 1-34.

\bibitem{Zaidman08}Zaidman A, Van Rompaey B, Demeyer S, et al. Mining software repositories to study co-evolution of production \& test code[C]//Software Testing, Verification, and Validation, 2008 1st International Conference on. IEEE, 2008: 220-229.

\bibitem{Nguyen13}Nguyen H A, Nguyen A T, Nguyen T T, et al. A study of repetitiveness of code changes in software evolution[C]//Proceedings of the 28th IEEE/ACM International Conference on Automated Software Engineering. IEEE Press, 2013: 180-190.

%no use
\bibitem{Ogheneovo14}Ogheneovo E E. On the relationship between software complexity and maintenance costs[J]. Journal of Computer and Communications, 2014, 2(14): 1-16 

\bibitem{Christa17}Christa S, Madhusudhan V, Suma V, et al. Software Maintenance: From the Perspective of Effort and Cost Requirement[C].//Proceedings of the International Conference on Data Engineering and Communication Technology. Singapore:Springer, 2017: 759-768

\bibitem{Alali08}Alali A, Kagdi H, Maletic J I. What's a typical commit? a characterization of open source software repositories[C].//Program Comprehension, 2008. ICPC 2008. The 16th IEEE International Conference on. Amsterdam:IEEE, 2008: 182-191

\bibitem{Casalnuovo13}Casalnuovo C. Analyzing and Generating Commit Messages for Software Repositories[D]. Newark:University of Delaware, 2013

\bibitem{Maalej10}Maalej W, Happel H J. Can development work describe itself?[C].//Mining Software Repositories (MSR), 2010 7th IEEE Working Conference on. Cape Town:IEEE, 2010: 191-200

\bibitem{Dyer13}Dyer R, Nguyen H A, Rajan H, et al. Boa: A language and infrastructure for analyzing ultra-large-scale software repositories[C].//Proceedings of the 2013 International Conference on Software Engineering. Piscataway:IEEE Press, 2013: 422-431

\bibitem{Santos16}Santos E A, Hindle A. Judging a commit by its cover: correlating commit message entropy with build status on travis-CI[C].//Mining Software Repositories. New York:IEEE, 2017:504-507

\bibitem{Dias15}Dias M, Bacchelli A, Gousios G, et al. Untangling fine-grained code changes[C].//Software Analysis, Evolution and Reengineering (SANER), 2015 IEEE 22nd International Conference on. Montreal:IEEE, 2015: 341-350

\bibitem{Tao15}Tao Y, Kim S. Partitioning composite code changes to facilitate code review[C].//Proceedings of the 12th Working Conference on Mining Software Repositories. Piscataway:IEEE Press, 2015: 180-190

\bibitem{zhouxiaocong18}周晓聪,赖蔚,温剑丰. 面向对象软件内聚度度量数据分布的实证研究[J]. 软件学报, 2017, 1(1): 1-18

\bibitem{Arafat09}Arafat O, Riehle D. The commenting practice of open source[C].//Proceedings of the 24th ACM SIGPLAN conference companion on Object oriented programming systems languages and applications. New York:ACM, 2009: 857-864

% 20 \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\bibitem{Schreck07}Schreck D, Dallmeier V, Zimmermann T. How documentation evolves over time[C].//Ninth international workshop on Principles of software evolution: in conjunction with the 6th ESEC/FSE joint meeting. New York:ACM, 2007: 4-10

\bibitem{Lawrie06}Lawrie D J, Feild H, Binkley D. Leveraged quality assessment using information retrieval techniques[C].//Program Comprehension, 2006. ICPC 2006. 14th IEEE International Conference on. Athens:IEEE, 2006: 149-158

\bibitem{McBurney16}McBurney P W, McMillan C. An empirical study of the textual similarity between source code and source code summaries[J]. Empirical Software Engineering, 2016, 21(1): 17-42



\bibitem{Tan12}Tan S H, Marinov D, Tan L, et al. @ tcomment: Testing javadoc comments to detect comment-code inconsistencies[C].//Software Testing, Verification and Validation (ICST), 2012 IEEE Fifth International Conference on. Montreal:IEEE, 2012: 260-269

\bibitem{Tan07}Tan L, Yuan D, Krishna G, et al. /* iComment: Bugs or bad comments?*[C].//ACM SIGOPS Operating Systems Review. New York:ACM, 2007, 41(6): 145-158

\bibitem{Malik08}Malik H, Chowdhury I, Tsou H M, et al. Understanding the rationale for updating a function’s comment[C].//Software Maintenance, 2008. ICSM 2008. IEEE International Conference on. Beijing:IEEE, 2008: 167-176

\bibitem{Sridhara16}Sridhara G. Automatically detecting the Up-To-Date status of ToDo comments in Java programs[C].//Proceedings of the 9th India Software Engineering Conference. New York:ACM, 2016: 16-25

\bibitem{Horwitz90}Horwitz S. Identifying the semantic and textual differences between two versions of a program[J]. Acm Sigplan Notices, 1990, 25(6):234-245

\bibitem{Chawathe96}Chawathe S S, Rajaraman A, Garcia-Molina H, et al. Change detection in hierarchically structured information[C].//ACM SIGMOD Record. New York:ACM, 1996, 25(2): 493-504

\bibitem{Fluri07}Fluri B, Wuersch M, Pinzger M, et al. Change Distilling:Tree Differencing for Fine-Grained Source Code Change Extraction[J]. IEEE Transactions on Software Engineering, 2007, 33(11):725-743

\bibitem{Gall09}Gall H C, Fluri B, Pinzger M. Change Analysis with Evolizer and ChangeDistiller[J]. IEEE Software, 2009, 26(1):26-33

\bibitem{Poshvvanvk09}Poshyvanyk D, Marcus A, Ferenc R, et al. Using information retrieval based coupling measures for impact analysis[J]. Empirical software engineering, 2009, 14(1): 5-32

\bibitem{Barnett15}Barnett M, Bird C, Brunet J, et al. Helping developers help themselves: Automatic decomposition of code review changesets[C].//Proceedings of the 37th International Conference on Software Engineering-Volume 1. Piscataway:IEEE Press, 2015: 134-144

\bibitem{Herziq13}Herzig K, Zeller A. The impact of tangled code changes[C].//Proceedings of the 10th Working Conference on Mining Software Repositories. Piscataway:IEEE Press, 2013: 121-130

\bibitem{Linares15}Linares-Vasquez M, Cortes-Coy L F, Aponte J, et al. Changescribe: A tool for automatically generating commit messages[C].//Software Engineering (ICSE), 2015 IEEE/ACM 37th IEEE International Conference on. Piscataway:IEEE, 2015:709-712

\bibitem{chenxinhe14}陈新河. 软件定义世界,数据驱动未来[J].软件产业与工程, 2014(01): 15-19


\bibitem{Hattori08}Hattori L P, Lanza M. On the nature of commits[C].//Proceedings of the 23rd IEEE/ACM International Conference on Automated Software Engineering. L'Aquila:IEEE Press, 2008: III-63


\bibitem{Guzman14}Guzman E, Azócar D, Li Y. Sentiment analysis of commit comments in GitHub: an empirical study[C].//Proceedings of the 11th Working Conference on Mining Software Repositories. New York:ACM, 2014: 352-355

\bibitem{Buse10}Buse R P L, Weimer W R. Automatically documenting program changes[C].//Proceedings of the IEEE/ACM international conference on Automated software engineering. New York:ACM, 2010: 33-42

\bibitem{Woodfield81}Woodfield S N, Dunsmore H E, Shen V Y. The effect of modularization and comments on program comprehension[C].//Proceedings of the 5th international conference on Software engineering. Piscataway:IEEE Press, 1981: 215-223

\bibitem{Ko06}Ko A J, Myers B A, Coblenz M J, et al. An exploratory study of how developers seek, relate, and collect relevant information during software maintenance tasks[J]. IEEE Transactions on software engineering, 2006, 32(12): 971-987

\bibitem{Tao12}Tao Y, Dang Y, Xie T, et al. How do software engineers understand code changes?: an exploratory study in industry[C].//Proceedings of the ACM SIGSOFT 20th International Symposium on the Foundations of Software Engineering. New York:ACM, 2012: 51-61

\bibitem{Souza05}de Souza S C B, Anquetil N, de Oliveira K M. A study of the documentation essential to software maintenance[C].//Proceedings of the 23rd annual international conference on Design of communication: documenting \& designing for pervasive information. New York:ACM, 2005: 68-75

\bibitem{Tenny88}Tenny T. Program readability: Procedures versus comments[J]. IEEE Transactions on Software Engineering, 1988, 14(9): 1271-1279

\bibitem{Takang96}Takang A A, Grubb P A, Macredie R D. The effects of comments and identifier names on program comprehensibility: an experimental investigation[J]. J. Prog. Lang., 1996, 4(3): 143-167

\bibitem{Nurvitadhi03}Nurvitadhi E, Leung W W, Cook C. Do class comments aid java program understanding?[C].//Frontiers in Education, 2003. FIE 2003 33rd Annual. Westminster:IEEE, 2003, 1: T3C-T3C

\bibitem{Steidl13}Steidl D, Hummel B, Juergens E. Quality analysis of source code comments[C].//Program Comprehension (ICPC), 2013 IEEE 21st International Conference on. San Francisco:IEEE, 2013: 83-92

\bibitem{Linares-Vasquez15}Linares-Vásquez M, Li B, Vendome C, et al. How do developers document database usages in source code?(N)[C].//Automated Software Engineering (ASE), 2015 30th IEEE/ACM International Conference on. Lincoln:IEEE, 2015: 36-41



%%%%

\bibitem{Hunt77}Hunt J W, Szymanski T G. A fast algorithm for computing longest common subsequences[J]. Communications of the ACM, 1977, 20(5): 350-353



\bibitem{Kitsu13}Kitsu E, Omori T, Maruyama K. Detecting program changes from edit history of source code[C].//Software Engineering Conference (APSEC), 2013 20th Asia-Pacific. Washington:IEEE Computer Society, 2013:299-306

\bibitem{Raghavan04}Raghavan S, Rohana R, Leon D, et al. Dex: A semantic-graph differencing tool for studying changes in large code bases[C].//Software Maintenance, 2004. Proceedings. 20th IEEE International Conference on. Chicago:IEEE, 2004: 188-197

\bibitem{Xing05}Xing Z, Stroulia E. UMLDiff: an algorithm for object-oriented design differencing[C].//Proceedings of the 20th IEEE/ACM international Conference on Automated software engineering. New York:ACM, 2005: 54-65


\bibitem{Maruvama12}Maruyama K, Kitsu E, Omori T, et al. Slicing and replaying code change history[C].//Automated Software Engineering (ASE), 2012 Proceedings of the 27th IEEE/ACM International Conference on. New York:ACM, 2012: 246-249

\bibitem{D'Ambros10}D'Ambros M, Lanza M, Robbes R. Commit 2.0[C].//Proceedings of the 1st Workshop on Web 2.0 for Software Engineering. New York:ACM, 2010: 14-19



\bibitem{Jiang06}Jiang Z M, Hassan A E. Examining the evolution of code comments in PostgreSQL[C].//Proceedings of the 2006 international workshop on Mining software repositories. New York:ACM, 2006: 179-180

\bibitem{Marin05}Marin D P. What motivates programmers to comment[J]. Technical Report No. UCB/EECS-2005018, University of California at Berkeley, 2005

\bibitem{Wursch07}Fluri B, Wursch M, Gall H C. Do code and comments co-evolve? on the relation between source code and comment changes[C].//Reverse Engineering, 2007. WCRE 2007. 14th Working Conference on. Vancouver:IEEE, 2007: 70-79

\bibitem{Fluri09}Fluri B, Würsch M, Giger E, et al. Analyzing the co-evolution of comments and source code[J]. Software Quality Journal, 2009, 17(4): 367-394

\bibitem{Ibrahim12}Ibrahim W M, Bettenburg N, Adams B, et al. On the relationship between comment update practices and software bugs[J]. Journal of Systems and Software, 2012, 85(10): 2293-2304





\bibitem{Rastkar13}Rastkar S, Murphy G C. Why did this code change?[C].// International Conference on Software Engineering. Piscataway:IEEE Press, 2013:1193-1196

\bibitem{Parnin08}Parnin C, Gorg C. Improving change descriptions with change contexts[C].//Proceedings of the 2008 international working conference on Mining software repositories. New York:ACM, 2008: 51-60




\bibitem{Moreno13}Moreno L, Marcus A, Pollock L, et al. Jsummarizer: An automatic generator of natural language summaries for java classes[C].//Program Comprehension (ICPC), 2013 IEEE 21st International Conference on. San Francisco:IEEE, 2013: 230-232

\bibitem{Wong15}Wong E, Liu T, Tan L. Clocom: Mining existing source code for automatic comment generation[C].//Software Analysis, Evolution and Reengineering (SANER), 2015 IEEE 22nd International Conference on. Montreal:IEEE, 2015: 380-389

\bibitem{Zanoni15}Zanoni M, Fontana F A, Stella F. On applying machine learning techniques for design pattern detection[J]. Journal of Systems and Software, 2015, 103: 102-117

\bibitem{Nguyen14}Nguyen A T, Nguyen H A, Nguyen T T, et al. Statistical learning approach for mining API usage mappings for code migration[C].//Proceedings of the 29th ACM/IEEE international conference on Automated software engineering. New York:ACM, 2014: 457-468

\bibitem{Mou16}Mou L, Li G, Zhang L, et al. Convolutional Neural Networks over Tree Structures for Programming Language Processing[J]. 2014:1287-1293



\bibitem{Lam15}Lam A N, Nguyen A T, Nguyen H A, et al. Combining deep learning with information retrieval to localize buggy files for bug reports (n)[C].//Automated Software Engineering (ASE), 2015 30th IEEE/ACM International Conference on. Lincoln:IEEE, 2015: 476-481

\bibitem{Ye16}Ye X, Shen H, Ma X, et al. From word embeddings to document similarities for improved information retrieval in software engineering[C].//Proceedings of the 38th international conference on software engineering. New York:ACM, 2016: 404-415

%chapter1 end.

%chapter2 begin.

\bibitem{Reddy00}Reddy A. Java coding style guide[J]. Sun MicroSystems, 2000, 1(5):8-10

\bibitem{Neamtiu05}Neamtiu I, Foster J S, Hicks M. Understanding source code evolution using abstract syntax tree matching[J]. ACM SIGSOFT Software Engineering Notes, 2005, 30(4): 1-5

\bibitem{Pascarella17}Pascarella L, Bacchelli A. Classifying code comments in Java open-source software systems[C].//Mining Software Repositories (MSR), 2017 IEEE/ACM 14th International Conference on. Buenos Aires:IEEE, 2017: 227-237

\bibitem{Pedersen04}Pedersen T, Patwardhan S, Michelizzi J. WordNet:: Similarity: measuring the relatedness of concepts[C].//Demonstration papers at HLT-NAACL 2004. Stroudsburg:Association for Computational Linguistics, 2004: 38-41

\bibitem{Bengio03}Bengio Y, Ducharme R, Vincent P, et al. A neural probabilistic language model[J]. Journal of machine learning research, 2003, 3(Feb): 1137-1155



\bibitem{Mikolov13}Mikolov T, Sutskever I, Chen K, et al. Distributed representations of words and phrases and their compositionality[C].//Advances in neural information processing systems. 2013: 3111-3119

\bibitem{Mikolov13-2}Mikolov T, Chen K, Corrado G, et al. Efficient estimation of word representations in vector space[J]. arXiv preprint arXiv:1301.3781, 2013

\bibitem{Quinlan86}Quinlan J R. Induction of decision trees[J]. Machine learning, 1986, 1(1): 81-106

\bibitem{Cortes95}Cortes C, Vapnik V. Support-vector networks[J]. Machine learning, 1995, 20(3): 273-297

\bibitem{Breiman01}Breiman L. Random forests[J]. Machine learning, 2001, 45(1): 5-32

\bibitem{He09}He H, Garcia E A. Learning from imbalanced data[J]. IEEE Transactions on knowledge and data engineering, 2009, 21(9): 1263-1284

%chapter2 end.

%chapter3 begin.
\bibitem{Hassan04}Hassan A E, Holt R C. Predicting change propagation in software systems[C].//Software maintenance, 2004. proceedings. 20th ieee international conference on. Chicago:IEEE, 2004: 284-293

\bibitem{fang11}方匡南,吴见彬,朱建平,谢邦昌.随机森林方法研究综述[J].统计与信息论坛, 2011, 26(03): 32-38

\bibitem{Conover98}Conover W. Practical Nonparametric Statistics[J]. Technometrics, 1974, 42(3): 317-318

%chapter3 end.
}
}
\end{thebibliography}


